---
title: "codebook"
author: "Mark Kushelman"
date: "March 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Variable list and descriptions
------------------------------
Note 1: below `u` means `mean` or `std`; `U` means `X`,`Y` or `Z`

Note 2: below the magnitude is calculated in the Euclidean norm

Variable name.          | Description
------------------------|------------
PERSON_ID               | The range is between 1 and 30.
ACTIVITY_NAME           | Activity name
tBodyAcc-u-U            | Feature: The `mean` or `std` time of the 3-dimension _body acceleration_ signals
tGravityAcc-u-U         | Feature: The `mean` or `std` time of the 3-dimension _gravity acceleration_ signals
tBodyAccJerk-u-U        | Feature: The `mean` or `std` time of the 3-dimension _body acceleration jerk_ signals
tBodyGyro-u-U           | Feature: The `mean` or `std` time of the 3-dimension _body gyroscope_ signals 
tBodyGyroJerk-u-U       | Feature: The `mean` or `std` time of the 3-dimension _body gyroscope jerk_ signals 
tBodyAccMag-u           | Feature: The `mean` or `std` time of the magnitude of the _body acceleration_ signals
tGravityAccMag-u        | Feature: The `mean` or `std` time of the magnitude of the _gravity acceleration_ signals
tBodyAccJerkMag-u       | Feature: The `mean` or `std` time of the magnitude of the _body acceleration jerk_ signals
tBodyGyroMag-u          | Feature: The `mean` or `std` time of the magnitude of the _body gyroscope_ signals     
tBodyGyroJerkMag-u      | Feature: The `mean` or `std` time of the magnitude of the _body gyroscope jerk_ signals
fBodyAcc-u-U            | Feature: The `mean` or `std` frequency of the 3-dimension _body acceleration_ signals
fBodyAccJerk-u-U        | Feature: The `mean` or `std` frequency of the 3-dimension _body acceleration jerk_ signals
fBodyGyro-u-U           | Feature: The `mean` or `std` frequency of the 3-dimension _body gyroscope_ signals
fBodyAccMag-u           | Feature: The `mean` or `std` frequency of the magnitude of the _body acceleration_ signals
fBodyBodyAccJerkMag-u   | Feature: The `mean` or `std` frequency of the magnitude of the __for me BodyBody does not have sense__ signals
fBodyBodyGyroMag-u      | Feature: The `mean` or `std` frequency of the magnitude of the __for me BodyBody does not have sense__ signals
fBodyBodyGyroJerkMag-u  | Feature: The `mean` or `std` frequency of the magnitude of the __for me BodyBody does not have sense__ signals
featCount               | Feature: Count of data points used to compute `average`
featAverage             | Feature: Average of each variable for each activity and each subject


```{r str}
str(dt_tidy_mean)
```

```{r key}
key(dt_tidy_mean)
```

```{r}
dt_tidy_mean
```

```{r summary}
summary(dt_tidy_mean)
```
