run_analysis
============
Last updated `r as.character(Sys.time())` using `r R.version$version.string`.

Instruction:
------------

1.  Execute steps 1 - 9
2.  Make script "makeCodebook.Rmd"
3.  Execute steps 1 - 10 (or only chunk 10 in RStudio) for creating codebook.md and codebook.html

1.Load packages
```{r Load packages, echo=TRUE, message=FALSE}
library(data.table); library(dplyr); library(knitr); library(markdown)
```

2.Get environment variables for pathes
```{r Get environment}
pathWD <- getwd()
DatasetDIR <- file.path(pathWD, "UCI HAR Dataset")
trainDIR <- file.path(DatasetDIR, "train")
testDIR <- file.path(DatasetDIR, "test")
```

3.Read the files
```{r Read files, echo=TRUE, message=FALSE, eval=TRUE}
f <- file.path(DatasetDIR, "activity_labels.txt"); activity_labels <- fread(f)
f <- file.path(DatasetDIR, "features.txt"); features <- fread(f)
f <- file.path(trainDIR, "subject_train.txt"); subject_train <- fread(f)
f <- file.path(testDIR, "subject_test.txt"); subject_test <- fread(f)
f <- file.path(trainDIR, "y_train.txt"); y_train <- fread(f)
f <- file.path(testDIR, "y_test.txt"); y_test <- fread(f) 
f <- file.path(trainDIR, "X_train.txt"); X_train <- fread(f)
f <- file.path(testDIR, "X_test.txt"); X_test <- fread(f)
rm(DatasetDIR, trainDIR, testDIR, f)
```

4.Set names
```{r}
setnames(activity_labels, names(activity_labels), c("ACTIVITY_ID","ACTIVITY_NAME"))
setnames(features, names(features), c("FEATURES_ID", "FEATURES_NAME"))
```

5.Leave features only with `mean()` and `std()`
```{r}
features <- features[grepl("mean\\(\\)|std\\(\\)", FEATURES_NAME)] 
features$FEATURES_CODE <- features[, paste0("V", FEATURES_ID)]
features$FEATURES_TIDY <- gsub("\\(\\)", "", features$FEATURES_NAME)
head(features)
```

6.Merge train and test sets by rows to create sets 
```{r}
subject <- rbind(subject_test,subject_train)
setnames(subject, names(subject), c("PERSON_ID"))

activity <- rbind(y_test,y_train)
setnames(activity, names(activity), c("ACTIVITY_ID"))

X <- rbind(X_test,X_train)
X <- cbind (X, subject, activity)
setkey(X, PERSON_ID, ACTIVITY_ID)
dim(X)
```

7.Select data from `X` only with `mean()` and `std()`
```{r}
dt <- select(X, PERSON_ID, ACTIVITY_ID, features$FEATURES_CODE)
dt <- merge(dt, activity_labels, by = "ACTIVITY_ID", all.x = TRUE)
dt <- select(dt, PERSON_ID, ACTIVITY_ID, ACTIVITY_NAME, features$FEATURES_CODE)
dim(dt)
names(dt)
head(dt, n = 3)
```

8.Prepare tidy data: dt_tidy
```{r}
dt_tidy <- dt
names(dt_tidy)[4:69] <- features$FEATURES_TIDY
dt_tidy$ACTIVITY_ID <- NULL
dt_tidy_mean <- dt_tidy %>% group_by (PERSON_ID, ACTIVITY_NAME) %>% summarize_all(funs(mean))
# setkey(dt_tidy_mean, PERSON_ID, ACTIVITY_NAME)
dim(dt_tidy_mean)
names(dt_tidy_mean)
head(dt_tidy_mean, n = 3)
```

9.Write the `dt_tidy_mean` into `tidy.txt` file
```{r}
write.table(dt_tidy_mean, file = "tidy.txt", sep = ",", row.name=FALSE) 
```

10.Make codebook
```{r}
knit("makeCodebook.Rmd", output="codebook.md", encoding="ISO8859-1", quiet=TRUE)
markdownToHTML("codebook.md", "codebook.html")
```

